\documentclass[main.tex]{subfiles}
\begin{document}

\section{Programing Basics} 
\label{sec:programing_basics}

\begin{frame}{Hello World}
	Let's start with a hello world program. See \textit{helloWorld.c}
	\begin{itemize}
		\item What's the main thing?
		\item Let's break something!
		\item Questions?
	\end{itemize}
\end{frame}

\section{Variables}
\label{sec:variables_scope_and_arrays}

\begin{frame}[fragile]{Variables - a Review}
	\begin{itemize}
		\item Containers for memory - why do we use variables in math?
		\item Types: What kind of data am I using?
		\item Syntax:
			\begin{lstlisting}
//a declaration
<type> <name>; 

//an instanciation 
// (which means "instance creation")
<name> = <value>;

//both at the same time
<type> <name>  = <value>;
			\end{lstlisting}
	\end{itemize}
\end{frame}

% section variables (end)

\section{Functions} 
\label{sec:functions}

\begin{frame}{Functions}
	\begin{itemize}
		\item Functions are used to modularize code
		\item Variables must be initialized at the top of the function.
	\end{itemize}
\end{frame}

\begin{frame}{Functions}
	\begin{itemize}
		\only<1->{
			\item Function in math: $\text{name}(\text{args}) = \text{stuff}$
			}
		\only<2->{\item Example: $foo(x,y) = x+y$}
		\only<3->{\item Some basic function syntax:}
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{Functions - An Example}
	Function Syntax
	\begin{lstlisting}
<type> name(<args>)
{

}
	\end{lstlisting}
Exmaple: 
		\begin{lstlisting}
double foo(double x, double y)
{
	return x+y;
}
		\end{lstlisting}
\end{frame}

\begin{frame}[fragile]{Functions and Scope}
Scope decides which variable to use when its used within some piece of code.

	\begin{lstlisting}[language=c]

int x = 0;

int f(int x)
{
	//which x is being used to calculate 
	//the result of this function?
	return (x+2);
}

int main(char argc, char** argv)
{
	int x = 0;
}

	\end{lstlisting}
\end{frame}

% section functions (end)

\section{Arrays}
\label{sec:arrays}

\begin{frame}[fragile]{Arrays}
	\begin{itemize}
		\item How can we store tables or lists of data? (pretend arrays didn't exist
			yet)
		\item Arrays - how we represent sets of data.
		\item Syntax:
			\begin{lstlisting}
<type> <name> [<size>];

<name>[<index>] = <value>;
			\end{lstlisting}
		\item why do indeces begin at 0?
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{Practical Use of Arrays}
	Calculating max height: see: \textit{arrays.c}
\end{frame}


\end{document}	
